---
title: "Adult Louvain Final Clusters ANOVAS"

output:
  html_document:
    number_sections: no
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, echo = F, include = F}
#load Libraries 
library(knitr)
library(dplyr)
library(purrr)
library(reshape2)
library(tidyr)
library(stringi)
library(ggplot2)
library(ggiraphExtra)
library(gplots)
library(heplots)
#install.packages("https://cran.r-project.org/src/contrib/Archive/hybridHclust/hybridHclust_1.0-5.tar.gz", repos = NULL, type = "source")
library(hybridHclust)
library(RColorBrewer)
library(viridis)
library(sjstats)

```

```{r, echo = F, include = F}

US_1 = read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Adult_Combined/Adult_US_Updated_07272020.csv", header = T, sep = ",")

UK_1 = read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Adult_Combined/Adult_UK_Updated_07272020.csv", header = T, sep = ",")

```

# ***Life Changes***

## US

### Difference 
```{r, warning = F, echo = F}
US_1$Louvain_Cluster_LC = as.factor(US_1$Louvain_Cluster_LC)
noCOVmodel <- aov(ew_difference ~ Louvain_Cluster_LC, data = US_1)

car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

### Emotion Worries Three Months 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries ~ Louvain_Cluster_LC, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### Emotion Worries Two Weeks 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries_2 ~ Louvain_Cluster_LC + emotion_worries, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### COVID Worries
```{r, warning = F, echo = F}

noCOVmodel <- aov(covid_worries ~ Louvain_Cluster_LC, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

## UK
### Difference 
```{r, warning = F, echo = F}
UK_1$Louvain_Cluster_LC = as.factor(UK_1$Louvain_Cluster_LC)
noCOVmodel <- aov(ew_difference ~ Louvain_Cluster_LC, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### Emotion Worries Three Months 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries ~ Louvain_Cluster_LC, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### Emotion Worries Two Weeks 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries_2 ~ Louvain_Cluster_LC + emotion_worries, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

   
# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

### COVID Worries
```{r, warning = F, echo = F}

noCOVmodel <- aov(covid_worries ~ Louvain_Cluster_LC, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons

pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_LC"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

# ***Behavior Media***

## US

### Difference 
```{r, warning = F, echo = F}
US_1$Louvain_Cluster_BM = as.factor(US_1$Louvain_Cluster_BM)
noCOVmodel <- aov(ew_difference ~ Louvain_Cluster_BM, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

### Emotion Worries Three Months 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries ~ Louvain_Cluster_BM, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

### Emotion Worries Two Weeks 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries_2 ~ Louvain_Cluster_BM + emotion_worries, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### COVID Worries
```{r, warning = F, echo = F}

noCOVmodel <- aov(covid_worries ~ Louvain_Cluster_BM, data = US_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)

```

## UK
### Difference 
```{r, warning = F, echo = F}
UK_1$Louvain_Cluster_BM = as.factor(UK_1$Louvain_Cluster_BM)
noCOVmodel <- aov(ew_difference ~ Louvain_Cluster_BM, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### Emotion Worries Three Months 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries ~ Louvain_Cluster_BM, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### Emotion Worries Two Weeks 
```{r, warning = F, echo = F}
noCOVmodel <- aov(emotion_worries_2 ~ Louvain_Cluster_BM + emotion_worries, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")

eta_sq(noCOVmodel)
```

### COVID Worries
```{r, warning = F, echo = F}

noCOVmodel <- aov(covid_worries ~ Louvain_Cluster_BM, data = UK_1)
car::Anova(noCOVmodel) %>%
   kable(format="pandoc")
# pairwise comparisons

# pairwise comparisons
pairs(emmeans::pmmeans(noCOVmodel, "Louvain_Cluster_BM"), adjust = "fdr") %>%
   kable(format="pandoc")


eta_sq(noCOVmodel)
```