---
title: "Subtype  Chi Square Tests"
output:
  html_document: default
  pdf_document: default
---

```{r, warning = F, echo = F, include=FALSE}
library(dplyr)
library(erer)
library(knitr)
library(purrr)
library(esc)
library(sjstats)
```

```{r, warning = F, echo = F,include=F}

UK <- read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Adult_Combined/Adult_UK_Updated_07272020.csv", header = T, sep = ",")[-1] 
US <- read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Adult_Combined/Adult_US_Updated_07272020.csv", header = T, sep = ",")[-1]
recoded_Crisis <- read.csv("C:/Users/jacob.derosa/Downloads/recoded_Crisis.csv", header = T, sep = ",")

Adult = rbind(US, UK) %>% select(-participant_id, -sample, -regsam, -retest, -hash_dup_id) %>%
  inner_join(recoded_Crisis, by=c("uid")) %>%
   mutate(age = ifelse(years < 30, "Under 30", 
                        ifelse(years >= 30 & years <= 49, "30-49", 
                               ifelse(years > 49, "Over 50", NA)))) %>%
  mutate(house_comp = ifelse(hhcomp == 0, "Living Alone", 
                             ifelse(hhcomp == 1, "Partner", 
                                    ifelse(hhcomp == 2 | hhcomp == 3, "Immediate no partner", 
                                           ifelse(hhcomp == 4, "Other", 
                                                  ifelse(hhcomp == 5 | hhcomp == 6, "Partner and Family", NA)))))) %>%
     mutate(Education = ifelse(education == 1 | education == 2, "Less High School", 
                                     ifelse(education == 3, "High School or GED", 
                                            ifelse(education == 4, "Some College or 2 year degree", 
                                                   ifelse(education == 5 | education == 6, "Some School beyond collge", 
                                                                 ifelse(education == 7, "Graduate or professional degree", NA)))))) %>% 
  mutate(newschool = as.factor(ifelse(schoolclosed == 1 & onlineclasses == 1, "onlineclasses",
                                              ifelse(schoolclosed == 0, "inpersonclasses",
                                                     ifelse(schoolclosed == 1 & onlineclasses == 0, "closesnoclass",
                                                            ifelse(schoolclosed == 2, "notapplicable", NA))))))

```

Adult US 
```{r, echo = F, include=T}

US = Adult %>% filter(sample == "Adult_US" | sample == "Adult_US_CA" | sample == "Adult_US_NY")

```

Run Chi-Sqaure Comparisons between US Life Changes Subtypes 
```{r}

#Filter Subtypes from Dataset
US_LC_1 = US %>% filter(Louvain_Cluster_LC == 1)
US_LC_2 = US %>% filter(Louvain_Cluster_LC == 2)
US_LC_3 = US %>% filter(Louvain_Cluster_LC == 3)

list = list(US_LC_1, US_LC_2, US_LC_3)
for(i in 1:length(list)){
  #Sex
  Sex_1 = table(list[[1]]$sex)[-3] #Keep only Males and Females 
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3) #Combine each subtype category 
  test = chisq.test(Sex_both) #Compute Chi-Square test 
  out <- data.frame("Sex p.value" = round(test$p.value, 3)) #Save P value 
  #Age
  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 3))
  #Race
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 3))
  #Rooms in House
  test.4 = aov(roomsinhouse ~ Louvain_Cluster_LC, data = US)
  out4 = summary(test.4)
  out4 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  #House Hold Density 
  test.5 = aov(hhdensity ~ Louvain_Cluster_LC, data = US)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))
  #Working (Job Loss)
  job_1 = table(list[[1]]$work)
  job_2 = table(list[[2]]$work)
  job_3 = table(list[[3]]$work)
  Job_Table = rbind(job_1, job_2, job_3)
  test.6 = chisq.test(Job_Table)
  out6 <- data.frame("job p.value" = round(test$p.value, 4))
  #School Closed 
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test.7 = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 4))
  
}

US_Adult_LC = data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Run Chi-Sqaure Comparisons between US Prior Habits Subtypes 
```{r, echo = F, include = T}

US_BM_1 = US %>% filter(Louvain_Cluster_BM == 1)
US_BM_2 = US %>% filter(Louvain_Cluster_BM == 2)
US_BM_3 = US %>% filter(Louvain_Cluster_BM == 3)

list = list(US_BM_1, US_BM_2, US_BM_3)
for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 3))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 3))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 3))
  
  test.6 = aov(roomsinhouse ~ Louvain_Cluster_BM, data = US)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_BM, data = US)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))

  job_1 = table(list[[1]]$work)
  job_2 = table(list[[2]]$work)
  job_3 = table(list[[3]]$work)
  Job_Table = rbind(job_1, job_2, job_3)
  test = chisq.test(Job_Table)
  out6 <- data.frame("job p.value" = round(test$p.value, 3))
  
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 3))
  
}

US_Adult_BM =  data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Adult UK 
```{r, echo = F, include=F}

UK = Adult %>% filter(sample == "Adult_London" | sample == "Adult_Manchester" | sample == "Adult_UK")

```

Run Chi-Sqaure Comparisons between UK Life Changes Subtypes 
```{r}
UK_LC_1 = UK %>% filter(Louvain_Cluster_LC == 1)
UK_LC_2 = UK %>% filter(Louvain_Cluster_LC == 2)
UK_LC_3 = UK %>% filter(Louvain_Cluster_LC == 3)

list = list(UK_LC_1, UK_LC_2, UK_LC_3)
for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 4))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 4))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 4))
  
  test.6 = aov(roomsinhouse ~ Louvain_Cluster_LC, data = UK)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_LC, data = UK)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))
  
  job_1 = table(list[[1]]$work)
  job_2 = table(list[[2]]$work)
  job_3 = table(list[[3]]$work)
  Job_Table = rbind(job_1, job_2)
  test = chisq.test(Job_Table)
  out6 <- data.frame("job p.value" = round(test$p.value, 4))
  
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 4))
  
  job_1 = table(list[[1]]$work)
  job_2 = table(list[[2]]$work)
  job_3 = table(list[[3]]$work)
  Job_Table = rbind(job_1, job_2, job_3)
  test = chisq.test(Job_Table)
  out6 <- data.frame("job p.value" = round(test$p.value, 4))
  
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 4))
  
}

UK_Adult_LC = data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq

#insert p, totaln, chisq from above output for each contingency table
esc_chisq(p =  3.538897e-06, 
          totaln = 884, 
          es.type = "eta", 
          chisq =  30.69132)

```

Run Chi-Sqaure Comparisons between UK Prior Habits Subtypes 
```{r, echo = F, include=F}

UK_BM_1 = UK %>% filter(Louvain_Cluster_BM == 1)
UK_BM_2 = UK %>% filter(Louvain_Cluster_BM == 2)
UK_BM_3 = UK %>% filter(Louvain_Cluster_BM == 3)

list = list(UK_BM_1, UK_BM_2, UK_BM_3)

for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 4))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 4))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 4))
  
  test.6 = aov(roomsinhouse ~ Louvain_Cluster_BM, data = UK)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_BM, data = UK)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))

  
  job_1 = table(list[[1]]$work)
  job_2 = table(list[[2]]$work)
  job_3 = table(list[[3]]$work)
  Job_Table = rbind(job_1, job_2, job_3)
  test = chisq.test(Job_Table)
  out6 <- data.frame("job p.value" = round(test$p.value, 4))
  
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 4))
  
}


UK_Adult_BM = data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}

eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Repeat steps below on Parent Data
```{r, echo = F}

UK_P <- read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Parent_Combined/Parent_UK_Updated_07272020.csv", header = T, sep = ",")[-1] 
US_P <- read.csv("C:/Users/jacob.derosa/Documents/Updated_Regsam_Splits/Updated_Datasets/Parent_Combined/Parent_US_Updated_07272020.csv", header = T, sep = ",")[-1]

recoded_Crisis <- read.csv("C:/Users/jacob.derosa/Downloads/recoded_Crisis.csv", header = T, sep = ",")

Parent = rbind(US_P, UK_P) %>% select(-participant_id, -sample, -regsam, -retest, -hash_dup_id) %>%
  inner_join(recoded_Crisis, by=c("uid")) %>%
   mutate(age = ifelse(years < 30, "Under 30", 
                        ifelse(years >= 30 & years <= 49, "30-49", 
                               ifelse(years > 49, "Over 50", NA)))) %>%
  mutate(house_comp = ifelse(hhcomp == 0, "Living Alone", 
                             ifelse(hhcomp == 1, "Partner", 
                                    ifelse(hhcomp == 2 | hhcomp == 3, "Immediate no partner", 
                                           ifelse(hhcomp == 4, "Other", 
                                                  ifelse(hhcomp == 5 | hhcomp == 6, "Partner and Family", NA)))))) %>%
  mutate(newschool = as.factor(ifelse(schoolclosed == 1 & onlineclasses == 1, "onlineclasses",
                                              ifelse(schoolclosed == 0, "inpersonclasses",
                                                     ifelse(schoolclosed == 1 & onlineclasses == 0, "closesnoclass",
                                                            ifelse(schoolclosed == 2, "notapplicable", NA)))))) %>%
  mutate(childage = ifelse(years_2 <= 5, "5_Under",
                           ifelse(years_2 > 5 & years_2 <=13, "6-13",
                                  ifelse(years_2 > 13 & years_2 <= 17, "13-17",
                                         ifelse(years_2 > 17, "18_over", NA)))))


```

Parent US 
```{r, echo = F, include=F}

US_P = Parent %>% filter(sample == "Parent_US" | sample == "Parent_US_CA" | sample == "Parent_US_NY")

```

Run Chi-Sqaure Comparisons between US Life Changes Subtypes 
```{r}

US_LC_1 = US_P %>% filter(Louvain_Cluster_LC == 1)
US_LC_2 = US_P %>% filter(Louvain_Cluster_LC == 2)
US_LC_3 = US_P %>% filter(Louvain_Cluster_LC == 3)

list = list(US_LC_1, US_LC_2, US_LC_3)

for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 4))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 4))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 4))
  
  test.4 = aov(roomsinhouse ~ Louvain_Cluster_LC, data = US_P)
  out4 = summary(test.4)
  out4 = data.frame("Rooms in House" = round(out4[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_LC, data = US_P)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))

  ChildAge_1 = table(list[[1]]$childage)
  ChildAge_2 = table(list[[2]]$childage)
  ChildAge_3 = table(list[[3]]$childage)
  ChildAge_Table = rbind(ChildAge_1, ChildAge_2, ChildAge_3)
  test.6 = chisq.test(ChildAge_Table)
  out6 <- data.frame("Child Age p.value" = round(test.6$p.value, 4))

  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test.7 = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test.7$p.value, 4))

  
}


US_P_Adult_LC = data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Run Chi-Sqaure Comparisons between US Prior Habits Subtypes 
```{r, echo = F}

US_BM_1 = US_P %>% filter(Louvain_Cluster_BM == 1)
US_BM_2 = US_P %>% filter(Louvain_Cluster_BM == 2)
US_BM_3 = US_P %>% filter(Louvain_Cluster_BM == 3)

list = list(US_BM_1, US_BM_2, US_BM_3)
for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 3))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 3))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 3))
  
  test.6 = aov(roomsinhouse ~ Louvain_Cluster_BM, data = US_P)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_BM, data = US_P)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))
  
  ChildAge_1 = table(list[[1]]$childage)
  ChildAge_2 = table(list[[2]]$childage)
  ChildAge_3 = table(list[[3]]$childage)
  ChildAge_Table = rbind(ChildAge_1, ChildAge_2, ChildAge_3)
  test.6 = chisq.test(ChildAge_Table)
  out6 <- data.frame("Child Age p.value" = round(test.6$p.value, 4))

 
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 3))

  
}


US_P_Adult_BM =  data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Parent UK
```{r, echo = F, include=F}

UK_P = Parent %>% filter(sample == "Parent_UK_London" | sample == "Parent_UK_Manchester" | sample == "Parent_UK")

```

Run Chi-Sqaure Comparisons between UK Life Changes Subtypes 
```{r}

UK_LC_1 = UK_P %>% filter(Louvain_Cluster_LC == 1)
UK_LC_2 = UK_P %>% filter(Louvain_Cluster_LC == 2)
UK_LC_3 = UK_P %>% filter(Louvain_Cluster_LC == 3)

list = list(UK_LC_1, UK_LC_2, UK_LC_3)
for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_Table = rbind(Sex_1, Sex_2, Sex_3)
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 3))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 3))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  Race_Table = rbind(R_1, R_2, R_3)
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 3))
  

  test.6 = aov(roomsinhouse ~ Louvain_Cluster_LC, data = UK_P)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_LC, data = UK_P)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))
   
  ChildAge_1 = table(list[[1]]$childage)
  ChildAge_2 = table(list[[2]]$childage)
  ChildAge_3 = table(list[[3]]$childage)
  ChildAge_Table = rbind(ChildAge_1, ChildAge_2, ChildAge_3)
  test.6 = chisq.test(ChildAge_Table)
  out6 <- data.frame("Child Age p.value" = round(test.6$p.value, 4))

  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  School_Table = rbind(school_1, school_2, school_3)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 3))

  
}

UK_P_Adult_LC =  data.frame(cbind(out, out2, out3, out4, out5, out6, out7))

```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```

Run Chi-Sqaure Comparisons between UK Prior Habits Clusters 
```{r, echo = F, include=F}

UK_BM_1 = UK_P %>% filter(Louvain_Cluster_BM == 1)
UK_BM_2 = UK_P %>% filter(Louvain_Cluster_BM == 2)
UK_BM_3 = UK_P %>% filter(Louvain_Cluster_BM == 3)
UK_BM_4 = UK_P %>% filter(Louvain_Cluster_BM == 4)

list = list(UK_BM_1, UK_BM_2, UK_BM_3, UK_BM_4)
for(i in 1:length(list)){
  
  Sex_1 = table(list[[1]]$sex)[-3]
  Sex_2 = table(list[[2]]$sex)[-3]
  Sex_3 = table(list[[3]]$sex)[-3]
  Sex_4 = table(list[[4]]$sex)[-3] 
  Sex_Table = data.frame(rbind(Sex_1, Sex_2, Sex_3, Sex_4))
  test = chisq.test(Sex_both)
  out <- data.frame("Sex p.value" = round(test$p.value, 4))

  Age_1 = table(list[[1]]$age)
  Age_2 = table(list[[2]]$age)
  Age_3 = table(list[[3]]$age)
  Age_4 = table(list[[4]]$age)
  Age_Table = rbind(Age_1, Age_2, Age_3, Age_4)
  test2 = chisq.test(Age_Table)
  out2 <- data.frame("Age p.value" = round(test2$p.value, 4))
  
  R_1 = t(as.matrix(table(list[[1]]$informant_race2)))
  R_2 = t(as.matrix(table(list[[2]]$informant_race2)))
  R_3 = t(as.matrix(table(list[[3]]$informant_race2)))
  R_4 = t(as.matrix(table(list[[4]]$informant_race2)))
  Race_Table = merge(R_1, R_2, all = T)
  Race_Table = merge(Race_Table, R_3, all = T)
  Race_Table = merge(Race_Table, R_4, all = T)
  Race_Table[is.na(Race_Table)] = 0
  test3 = chisq.test(Race_Table)
  out3 <- data.frame("Race p.value" = round(test3$p.value, 4))
  
  DX_1 = table(list[[1]]$fam_dx)
  DX_2 = table(list[[2]]$fam_dx)
  DX_3 = table(list[[3]]$fam_dx)
  DX_4 = table(list[[4]]$fam_dx)
  DX_both = rbind(DX_1, DX_2, DX_3, DX_4)
  test5 = chisq.test(DX_both)
  out5 <- data.frame("Fam DX p.value" = round(test5$p.value, 4))
  
  test.6 = aov(roomsinhouse ~ Louvain_Cluster_BM, data = UK_P)
  out6 = summary(test.6)
  out6 = data.frame("Rooms in House" = round(out6[[1]][["Pr(>F)"]][1],4))
  
  test.5 = aov(hhdensity ~ Louvain_Cluster_BM, data = UK_P)
  out5 = summary(test.5)
  out5 = data.frame("HH Density" = round(out5[[1]][["Pr(>F)"]][1],4))

  
  school_1 = table(list[[1]]$newschool)
  school_2 = table(list[[2]]$newschool)
  school_3 = table(list[[3]]$newschool)
  school_4 = table(list[[4]]$newschool)
  School_Table = rbind(school_1, school_2, school_3, school_4)
  test = chisq.test(School_Table)
  out7 <- data.frame("school p.value" = round(test$p.value, 4))
  
  ChildAge_1 = table(list[[1]]$childage)
  ChildAge_2 = table(list[[2]]$childage)
  ChildAge_3 = table(list[[3]]$childage)
  ChildAge_4 = table(list[[4]]$childage)
  ChildAge_Table = rbind(ChildAge_1, ChildAge_2, ChildAge_3, ChildAge_4)
  test.6 = chisq.test(ChildAge_Table)
  out6 <- data.frame("Child Age p.value" = round(test.6$p.value, 4))
  
}

UK_P_Adult_BM =  data.frame(cbind(out, out2, out3, out4, out5, out6, out7))


```

ANOVA ETA Squared Calculation 
```{r}
eta_sq(test.4) #Anova eta hhdensity 
eta_sq(test.5) #Anova eta 

```

Chi-Square ETA Calculation on Contingency Tables
```{r}
#Options for ct =  (Job_Table, School_Table, Race_Table, Age_Table, Sex Both )
ES.chisq.assoc(ct = Job_Table) #obtain p, totaln, chisq
esc_chisq(p =   5.157132e-08, 
          totaln = 886, 
          es.type = "eta", 
          chisq =  39.63205)

```




