---
title: "RandomForest"
author: "Aki Nikolaidis,Ian Douglas, Jacob DeRosa"
date: "5/3/2020"
output: html_document
---

```{r, results='hide', message=FALSE}
set.seed(111)
if (!require(tidyverse)) {install.packages("tidyverse")}
if (!require(readxl)) {install.packages("readxl")}
if (!require(doParallel)) {install.packages("doParallel")}
if (!require(randomForest)) {install.packages("randomForest")}

library(readxl)
library(doParallel)
library(randomForest)
library(tidyverse)
library(ggplot2)
library(viridis)
library(corrplot)
library(knitr)
library(REdaS) # for diagnostic data checks before FA
library(psych) # need for factor analysis
library(GPArotation) # need for factor analysis
library(polycor)
library(lavaan)
library(sjmisc)
library(gtools)
```





#DATA ORGANIZATION
```{r Data_Organization}
#full_dataset <- read.csv('/Users/aki.nikolaidis/Dropbox/1_Projects/1_Research/CRISIS/Data/FullSample/working_data_20200424.csv', header = TRUE, sep = ",")

full_dataset <- read.csv('/Users/aki.nikolaidis/Dropbox/1_Projects/1_Research/CRISIS/Data/UpdatedRace/Working_Data/Parent_US_Updated_07272020.csv', header = TRUE, sep = ",")


#prediction_data <- read.csv('/Users/aki.nikolaidis/Dropbox/1_Projects/1_Research/CRISIS/Data/Difference_Scores/US_Split_1_diff_df.csv', header = TRUE, sep = ",")

# set output folder for plots, based on date
sample <- 'US_Parent_Combined'
#CHOICES:
#         US_Adult1
#         UK_Adult1
#         US_Parent1
#         UK_Parent1

analysis <-'final_FULL_MODEL'

number_of_bootstraps <- 1000


analysis_name <- paste0(sample, '/', analysis)

todays_date <- Sys.Date()

dir.create(paste0('../plots/'))
dir.create(paste0('../plots/',sample))
dir.create(paste0('../plots/',sample,'/',analysis))

dir.create(paste0('../output/',sample))
dir.create(paste0('../output/',sample,'/',analysis))

#Background:
#location:43
#education : 44
#educationmother: 45
#educationfather: 46
#householdnumber: 47
#essentialworkers: 48
#roomsinhouse: 58
#insurance: 59
#govassist: 60
#physicalhealth: 61

match('years_2', names(full_dataset))


# covid_worries: 303
# covid_worries_resid: 304
# ew_difference_resid: 305
# emotion_worries_resid: 306
# emotion_worries_2_resid: 307
# emotion_worries: 308
# emotion_worries_2: 309
# ew_difference: 310
# Louvain_Cluster_LC: 315 #Updated
# Louvain_Cluster_BM: 314 #Updated
# Final Race variable: 316

#Need to make updates to data file:
#Positive change at 292

### ADULT DATA BASELINE + Life Changes + COVID#####

#BASELINE, dropping 303 (COVID Worries), 315 (LC Subtype)
#domain_data <- full_dataset[,c(2, 9, 43:48, 58:61, 142:147,158:160, 161:167, 235, 308, 316)]

#BASELINE + LC Subtype ____________dropping 303 (COVID WOrries)
#domain_data <- full_dataset[,c(2, 9, 43:48, 58:61, 142:147,158:160, 161:167, 235, 308, 315, 316)]

#BASELINE + COVID ________________dropping 315 (LC Subtype)
#domain_data <- full_dataset[,c(2, 9, 43:48, 58:61, 142:147,158:160, 161:167, 235, 303, 308, 316)]

#FULL MODEL
#domain_data <- full_dataset[,c(2, 9, 43:48, 58:61, 142:147,158:160, 161:167, 235,303, 308, 315, 316)]




### PARENT DATA BASELINE + Life Changes + COVID#####
#226:229


#BASELINE, dropping 303 (COVID Worries), 315 (LC Subtype)
#domain_data<- full_dataset[,c(2, 215, 43,47,48, 58:61, 226:229, 146:147,158:160, 161:167, 235, 308, 316)]

#BASELINE + LC Subtype ____________dropping 303 (COVID WOrries)
#domain_data <- full_dataset[,c(2, 215, 43,47:48, 58:61, 226:229, 146:147,158:160, 161:167, 235, 308,315, 316)]

#BASELINE + COVID ________________dropping 315 (LC Subtype)
#domain_data <- full_dataset[,c(2,215, 43,47:48, 58:61, 226:229, 146:147,158:160, 161:167, 235,303, 308, 316)]


#FULL MODEL
domain_data <- full_dataset[,c(2,215, 43,47:48, 58:61, 226:229, 146:147,158:160, 161:167, 235,303, 308,315, 316)]
names(domain_data)[which(names(domain_data) == "years_2")] <- "years"

domain_data<-domain_data[complete.cases(domain_data),]

emotion_worries_temp_factor<-quantcut(domain_data$emotion_worries,5)

factor_emotion_worries<-domain_data$emotion_worries
emotion_worries_levels <-levels(emotion_worries_temp_factor) 
factor_emotion_worries[emotion_worries_temp_factor==emotion_worries_levels[1]]<-1
factor_emotion_worries[emotion_worries_temp_factor==emotion_worries_levels[2]]<-2
factor_emotion_worries[emotion_worries_temp_factor==emotion_worries_levels[3]]<-3
factor_emotion_worries[emotion_worries_temp_factor==emotion_worries_levels[4]]<-4
factor_emotion_worries[emotion_worries_temp_factor==emotion_worries_levels[5]]<-5
factor_emotion_worries<-as.factor(factor_emotion_worries)

years_temp_factor<-quantcut(domain_data$years,5)
factor_years<-domain_data$years
years_levels <-levels(years_temp_factor)
factor_years[years_temp_factor==years_levels[1]]<-1
factor_years[years_temp_factor==years_levels[2]]<-2
factor_years[years_temp_factor==years_levels[3]]<-3
factor_years[years_temp_factor==years_levels[4]]<-4
factor_years[years_temp_factor==years_levels[5]]<-5
factor_years<-as.factor(factor_years)

#Comment out below for baseline model, and baseline + LC Model

covid_worries_temp_factor<-quantcut(domain_data$covid_worries,5)
factor_covid_worries<-domain_data$covid_worries
covid_worries_levels <-levels(covid_worries_temp_factor)
factor_covid_worries[covid_worries_temp_factor==covid_worries_levels[1]]<-1
factor_covid_worries[covid_worries_temp_factor==covid_worries_levels[2]]<-2
factor_covid_worries[covid_worries_temp_factor==covid_worries_levels[3]]<-3
factor_covid_worries[covid_worries_temp_factor==covid_worries_levels[4]]<-4
factor_covid_worries[covid_worries_temp_factor==covid_worries_levels[5]]<-5
factor_covid_worries<-as.factor(factor_covid_worries)


# Baseline Model, Baseline + LC Subtype
#domain_data <-cbind(domain_data, factor_emotion_worries, factor_years)
#domain_data = subset(domain_data, select = -c(emotion_worries, years))

# Full Model, Baseline + COVID Worries
domain_data <-cbind(domain_data, factor_emotion_worries, factor_covid_worries, factor_years)
domain_data = subset(domain_data, select = -c(covid_worries, emotion_worries, years))











#behavior_media <- full_dataset[,c(142:147,158:160)]
#emotions_worries <- full_dataset[,c(148:157)]
#substance_use <- full_dataset[,c(161:167)]

prediction_data <- full_dataset[,c(2, 309)]
prediction_data<-prediction_data[complete.cases(prediction_data),]

index1<-t(domain_data$participant_id) %in% t(prediction_data$participant_id)
domain_data<-domain_data[index1,]

index2<-t(prediction_data$participant_id) %in% t(domain_data$participant_id)
prediction_data<-prediction_data[index2,]


all_data = merge(domain_data, prediction_data, by = "participant_id")

all_data = all_data[complete.cases(all_data),]
domain_data <- all_data


```


#Background data, 3 months data, COVID worries factor, life changes cluster
#BACKGROUND <- full_dataset[,c(43:48, 58:61)]

# PARENT COMBINED: full_dataset[,c(225:228,146,147,158:160,148:157,161:167,109:113,141, 114,128:140)]
#ADULT COMBINED: full_dataset[,c(142:147,158:160,148:157,161:167,109:113,141, 114,128:140)]

#COVID WOrries
#covid_worries <- full_dataset[,c(109:113,141)]
#life_changes <- full_dataset[,c(114,128:140)]

# PARENT REPORT
#behavior_media <- full_dataset[,c(225:228,146,147,158:160)]
#emotions_worries <- full_dataset[,c(148:157)]
#substance_use <- full_dataset[,c(161:167)]


#ADULT SELF REPORT
#behavior_media <- full_dataset[,c(142:147,158:160)]
#emotions_worries <- full_dataset[,c(148:157)]
#substance_use <- full_dataset[,c(161:167)]






# Fit the model
```{r Fit the model}
rf_domain = randomForest(
  formula = emotion_worries_2 ~ .-participant_id,
  data = all_data,
  mtry = round((ncol(all_data) - 4)/3),
  ntree = 1000,
  #strata = rf_data$Upbringing_Group,
  replace = TRUE,
  #sampsize = min(table(data_for_cbcl_rf$Upbringing_Group)) * n_distinct(data_for_cbcl_rf$Upbringing_Group),
  proximity = TRUE, 
  localImp = TRUE, 
  importance = TRUE
)

domain_r_squared=cor(rf_domain$predicted,rf_domain$y)**2
rf_lm<-lm(rf_domain$y ~ rf_domain$predicted)
logLik(rf_lm)
saveRDS(rf_domain, file= paste0("../output/",analysis_name,"/1_domainTotal.rds"))
cbind
tempdata <- data.frame(cbind(rf_domain$y, rf_domain$predicted))

library(ggplot2)
# Basic scatter plot
ggplot(tempdata, aes(x=X1, y=X2)) + geom_point()
scatter<-ggplot()+
  geom_point(x=rf_domain$predicted, y = rf_domain$y)
scatter

#CREATE NULL domain MODEL
reruns<-1:5#1000#
domain_mean_rsq_vec<-vector()
domain_predict_actual_rsq<-vector()
null_rf_data<- all_data
null_rf_data<-subset(null_rf_data, select= -c(emotion_worries_2))

for (i in seq_along(reruns)){
  shuffled_y_target<-sample(all_data$emotion_worries_2)
  null_rf_data<-cbind(null_rf_data,shuffled_y_target)
  
  
  NULL_rf_domain_TOTAL = randomForest(
  formula = shuffled_y_target ~ .-participant_id,
  data = null_rf_data,
  mtry = round((ncol(null_rf_data) - 4)/3),
  ntree = 1000,
  #strata = null_rf_data$Upbringing_Group,
  replace = TRUE,
  #sampsize = min(table(null_rf_data$Upbringing_Group)) * n_distinct(null_rf_data$Upbringing_Group),
  proximity = TRUE, 
  localImp = TRUE, 
  importance = TRUE)
  
  domain_mean_rsq_vec<-append(domain_mean_rsq_vec,mean(NULL_rf_domain_TOTAL$rsq))
  domain_predict_actual_rsq <- append(domain_predict_actual_rsq,
                                    (cor(NULL_rf_domain_TOTAL$predicted,NULL_rf_domain_TOTAL$y))**2)

  null_rf_data<-subset(null_rf_data, select = -c(shuffled_y_target))
}
```

#Plot Results
```{r Plot Results}
nulldata_rsq <-data.frame("nullrsq" = domain_predict_actual_rsq)

nullstats95<-t.test(nulldata_rsq$nullrsq,conf.level = 0.95)
nullstats99<-t.test(nulldata_rsq$nullrsq,conf.level = 0.99)
nullstats999<-t.test(nulldata_rsq$nullrsq,conf.level = 0.999)
nullstats999999<-t.test(nulldata_rsq$nullrsq,conf.level = 0.999999)
nullmean<-nullstats95$estimate

domain_v_null <- ggplot(nulldata_rsq, aes(y=nullrsq)) +
    ylim(0,0.6) +
    geom_jitter(aes(x="Null Model Distribution", y=nullrsq), alpha = 0.2, size = 0.1) +

    geom_hline(yintercept=nullstats95$estimate, color = "blue") +
    geom_hline(yintercept=max(nullstats999999$conf.int), color = "red") +

    geom_point(aes(x="Null Model Distribution", y=domain_r_squared), size = 6, shape = 23, color = "black", fill = "purple") + 
    annotate("text", x ="Null Model Distribution", y=(nullstats95$estimate - 0.005), label = "Null Model Mean")+
    annotate("text", x ="Null Model Distribution", y=(max(nullstats999999$conf.int)+ 0.02), label = "99.9999% CI")+
    annotate("text", x ="Null Model Distribution", y=(domain_r_squared + 0.03), label = "Model Performance") +
    theme_classic() +
  ylab("R-Squared")

ggsave(domain_v_null, height = 5, width = 3, file = paste0("../plots/", analysis_name,  
       "/RF_domain_Tot_vNull.png"))

```



# Variable importance plot
```{r Variable importance plot}
# merge the variable importances with their respective SD to compute error bars

#rf_domain<- readRDS(file="/Users/aki.nikolaidis/Dropbox/1_Projects/1_Research/CRISIS/output/US_Parent_Combined/final_LC-Clust_COVID_background_prediction/1_domainTotal.rds")

#rf_domain<- readRDS(file="/Users/aki.nikolaidis/Dropbox/1_Projects/1_Research/CRISIS/output/UK_Adult_Combined/final_EmWor_LC-Clust_COVID_background_prediction/1_domainTotal.rds")

#US Adult
#UK Adult
#US Parent
#UK Parent


VIMs = merge(
  as.data.frame(importance(rf_domain)) %>%
    mutate(Variable = rownames(importance(rf_domain))) %>%
    rename(PercentChangeMSE = `%IncMSE`) %>%
    select(-IncNodePurity),
  data.frame(Variable = names(rf_domain$importanceSD),
             importanceSD = rf_domain$importanceSD),
  by = "Variable"
) %>%
  mutate(# the importances are divided by their SD, so return them to original scale:
    PercentChangeMSE = PercentChangeMSE * importanceSD,
    VIM_upr = PercentChangeMSE + 2*importanceSD,
    VIM_lwr = PercentChangeMSE - 2*importanceSD) %>%
  arrange(desc(PercentChangeMSE)) %>%
  # finally, multiply all percent values by 100%, since they are in decimal form now
  mutate_if(is.numeric, ~(. * 100))
# order the factor labels to be in descending order (as the data frame is ordered already)
VIMs$Variable = factor(VIMs$Variable,
                       levels = rev(VIMs$Variable))


VIMs = mutate(VIMs, select(VIM_lwr))

# Set variable labels to be correct text
#ADULT SELF REPORT
 # VIMs = mutate(VIMs,
 #                Variable = case_when(Variable == 'factor_covid_worries' ~'COVID Worries',
 #                               Variable == 'bedtimeweekdays' ~ 'Weekday Bedtime',
 #                               Variable == 'priortvmedia' ~ 'TV Usage',
 #                               Variable == 'factor_emotion_worries' ~ 'Prior Mood States',
 # 
 #                               Variable == 'Louvain_Cluster_LC' ~ 'Life Changes Subtype',
 #                               Variable == 'bedtimeweekends' ~ 'Weekend Bedtime',
 #                               Variable == 'exerciseprior' ~ 'Exercise',
 #                               Variable == 'threemonthsalcohol' ~ 'Alcohol',
 #                               Variable == 'insurance' ~ 'Insurance',
 #                               Variable == 'threemonthsvaping' ~ 'Vaping',
 #                               Variable == 'education' ~ 'Education',
 #                               Variable == 'outdoorsprior' ~ 'Outdoors',
 #                               Variable == 'informant_race2' ~ 'Race',
 #                               Variable == 'location' ~ 'Location',
 #                               Variable == 'hoursofsleepweekdays' ~ 'Weekday Sleep',
 #                               Variable == 'educationfather' ~ 'Father Education',
 #                               Variable == 'educationmother' ~ 'Mother Education',
 #                               Variable == 'householdnumber' ~ 'Household Number',
 #                               Variable == 'priorvideogames' ~ 'Videogames',
 #                               Variable == 'factor_years' ~ 'Age',
 #                               Variable == 'hoursofsleepweekends' ~ 'Weekend Sleep',
 #                               Variable == 'roomsinhouse' ~ 'Rooms in House',
 #                               Variable == 'physicalhealth' ~ 'Physical Health',
 #                               Variable == 'priorsocialmedia' ~ 'Social Media',
 #                               Variable == 'threemonthstobacco' ~ 'Tobacco',
 #                               Variable == 'threemonthsmarijuana' ~ 'Marijuana',
 #                               Variable == 'threemonthsopiates' ~ 'Opiates',
 #                               Variable == 'essentialworkers' ~ 'Essential Workers',
 #                               Variable == 'govassist' ~ 'Gov. Assistance',
 #                               Variable == 'threemonthsother' ~ 'Other Drugs',
 #                               Variable == 'sex_cat' ~ 'Sex',
 #                               Variable == 'threemonthssleepingmeds' ~ 'Sleeping Meds'))  %>%
 #              arrange(desc(PercentChangeMSE))


#PARENT REPORT

VIMs = mutate(VIMs,
               Variable = case_when(Variable == 'factor_covid_worries' ~'COVID Worries',
                              Variable == 'priorweekdaybedtime' ~ 'Weekday Bedtime',
                              Variable == 'priortvmedia' ~ 'TV Usage',
                              Variable == 'factor_emotion_worries' ~ 'Prior Mood States',
                              Variable == 'Louvain_Cluster_LC' ~ 'Life Changes Subtype',
                              Variable == 'priorweekendbedtime' ~ 'Weekend Bedtime',
                              Variable == 'factor_years' ~ 'Age',
                              Variable == 'exerciseprior' ~ 'Exercise',
                              Variable == 'threemonthsalcohol' ~ 'Alcohol',
                              Variable == 'insurance' ~ 'Insurance',
                              Variable == 'threemonthsvaping' ~ 'Vaping',
                              Variable == 'education' ~ 'Education',
                              Variable == 'outdoorsprior' ~ 'Outdoors',
                              Variable == 'informant_race2' ~ 'Race',
                              Variable == 'location' ~ 'Location',
                              Variable == 'priorhoursofsleepweekdays' ~ 'Weekday Sleep',
                              Variable == 'educationfather' ~ 'Father Education',
                              Variable == 'educationmother' ~ 'Mother Education',
                              Variable == 'householdnumber' ~ 'Household Number',
                              Variable == 'priorvideogames' ~ 'Videogames',
                              Variable == 'years' ~ 'Age',
                              Variable == 'priorhoursofsleepweekend' ~ 'Weekend Sleep',
                              Variable == 'roomsinhouse' ~ 'Rooms in House',
                              Variable == 'physicalhealth' ~ 'Physical Health',
                              Variable == 'priorsocialmedia' ~ 'Social Media',
                              Variable == 'threemonthstobacco' ~ 'Tobacco',
                              Variable == 'threemonthsmarijuana' ~ 'Marijuana',
                              Variable == 'threemonthsopiates' ~ 'Opiates',
                              Variable == 'essentialworkers' ~ 'Essential Workers',
                              Variable == 'govassist' ~ 'Gov. Assistance',
                              Variable == 'threemonthsother' ~ 'Other Drugs',
                              Variable == 'sex_cat' ~ 'Sex',
                              Variable == 'threemonthssleepingmeds' ~ 'Sleeping Meds'))  %>%
              arrange(desc(PercentChangeMSE))


VIMs$Variable = factor(VIMs$Variable,
                       levels = rev(VIMs$Variable))


# Plotting:
plt = ggplot(data = VIMs) +
  geom_bar(stat= "identity", aes(x = Variable, y = PercentChangeMSE), fill = 'lightgrey') +
  geom_errorbar(aes(x = Variable, ymin = VIM_lwr, ymax = VIM_upr)) +
  coord_flip() +
  theme_linedraw() +
  ggtitle("Variable Importances For Predicting Change Emotions Worries",
          subtitle = paste("% variance explained: ", domain_r_squared)) +
  theme(
    plot.subtitle = element_text(size=22, hjust = .5),
    title = element_text(hjust = .5, size = 25),
    axis.title = element_text(size=20),
    axis.text = element_text(size = 15)
  ) +
  ylab("Percent Change in MSE")


ggsave(plt, height = 12, width = 15, file = paste0("../plots/", analysis_name,  
       "/Importance_RF_Total2.png"))
       

#ggsave(plot = plt, 
#       file= paste0("../../finalPlots/", todays_date, "/randomForest/final/VIMPlot_RF_rawECA+5PC_regressCBCLTOTAL.png"),
#       height = 12, width = 15)



```

